Operationally-Safe Peer-to-Peer Energy Trading in Distribution Grids: A Game-Theoretic Market-Clearing Mechanism

### 2021-12-17 papers/01 Reply round 1/response_TSG.tex

We have also modified our game formulation and proposed algorithm in Section III to take into account this storage model update.

\query[R1-4]{The energy loss of the distribution network is also not considered.}
\ans{We do not include energy loss of the distribution network in the current setup and leave it for future work. In this manuscript, we focus on the game-theoretic formulation of the interaction among prosumers and the network operator and show that the problem can be solved efficiently. Based on the formulation in our manuscript, the energy loss can be included as long as it is formulated as \comment{continue depending whether this appears in the cost function or constraints}}

@@

\query[R1-5]{The individual variables, coupled relationships for these energy roles, and the corresponding dual variables should be explained specifically, along with the whole framework structure for equilibrium. The rationalities of the framework is not clear. At least, the current presentation is hard to follow.  }
\ans{}

\query[R1-6]{The P2P trading prices are given parameters, which are quite unreasonable. In fact, the P2P prices are the key variable in most literature.}
\ans{In this manuscript, we want to consider the most general problem formulation available in the literature. Following \cite{sorin2019,lecadre2020,sousa2019}, a linear trading cost function is introduced in the problem formulation to describe \comment{continue}. Furthermore, \cite{bibid} also adds a trading tariff encoded as a 1-norm cost function. Furthermore, we may set $c_{\{i,j\}}^{\mathrm{tr}}=0$, and thus only consider the dual variable associated with the reciprocity constraints (Eq. \red{(xx)} in the revised manuscript) as the shadow price of trading. Indeed the proposed algorithm can handle any case where $c_{\{i,j\}}^{\mathrm{tr}} \geq 0$, for all $\{i,j\} \in \mc E$.}

@@

\query[R3-3]{As well pointed by the authors, this is a semi-decentralized approach where a coordinator is needed. Please, provide some discussion on how this is different with community-based local markets.   }
\ans{As discussed in \cite[Sect. 3.2]{sousa2019}, in community-based local markets, each prosumer  does not know with which other prosumers it trades energy. The power balance of the whole network (all prosumers) is considered. Our setup considers full P2P markets where each prosumer knows its trading partners and, thus, negotiates directly with them. The coordinator in our setup plays a role in handling the physical constraints of the network as well as the aggregated power bought from the main grid.}

\query[R3-4]{ The proposed algorithm relies on several dual variables. Please, elaborate on the meaning of this dual variables and their interpretation as economic outputs of the clearing process. }
\ans{\comment{apply comment}}

\query[R3-5]{As to the results section, I miss some analysis of trading prices. Please consider to add some information about transactions prices among peers and compare them with grid prices. This analysis might be interesting in both storage and non-storage situations.}
\ans{\comment{apply comment}}

\query[R3-6]{ Please, check Figure 7. The authors claim that storage help in shaving the peak of total power imported from the main grid, but this looks the same in both figures.  }
\ans{We thank the Reviewer for providing this observation. What we claim is that the storage shaves the peak of the sum of the total power imported from the main grid and that of locally generated power. Indeed, due to the choice of the cost parameters, which follows \cite{atzeni2013}, local generation costs are cheaper than importing cost. We have redone the simulations where we readjust the cost parameters and introduce a positive quadratic coefficient on $f_i^{\mathrm{di}}$. Due to this adjustment, we can now see in Figure \red{xx} in the revised manuscript (as also shown below) that the storage particularly shaves the peak of total power imported from the main grid.  \comment{show the new figure}}

@@

\query[R4-4]{ Related to the previous comment, one of the nonlinearities appears in the objective function related to dispatchable units (equation (2)). However, in the numerical studies the parameter $Q_{i}^{di}$ is taken as zero, becoming a linear objective function, and simplifying the model. The same happens with the objective function associated to storage units (equation (4)). Have you tested the effect of these parameters in the model? Further, if these parameters take a positive value, some of the conclusions presented in the numerical study could change. I suggest the authors to analyze this issue.  }
\ans{\comment{Wicak} \comment{nonlinear objective function is not an issue. Show simulation results here when we have strongly convex cost of storage and dispatchable units. We follow existing paper for the parameters of problem. }}

\query[R4-5]{The objective function associated to the power traded with the main grid seems not so natural. If the electricity unit price, $c_{h}^{mg}$ in equation (9) is considered linear (instead of quadratic) with respect to the total consumption, this would simplify this term, further becoming (11) a decomposable function. Could the authors elaborate what is the advantage of using a quadratic term here? Is worth the improvement it could add with respect to the difficulty it brings to the model?}
\ans{\comment{Wicak} \comment{correspond to linear inverse demand function}}

\query[R4-6]{ Taking into account comment 1, suppose that we consider a reformulation of the problem to avoid coupling objective functions, and we employ the Alternating Direction Methods of Multipliers (ADMM) to solve the P2P market game in (1). Could the authors elaborate if this would be possible? Would the application of the ADDM also guarantees the convergence to a variational GNE of the P2P market game? What are the advantages of using Algorithm 1 proposed in the paper to solve the problem?  }
\ans{}

\query[R4-7]{ Regarding to the scalability of the algorithms, the author evaluates the convergence of the algorithm with respect to the number of agents and the connectivity, but they do not provide any information about the computational times. This is relevant to evaluate if it could be applied in a real large-scale system. }
\ans{We thank the Reviewer for raising this point. We agree that the computational time is relevant in practice and thus we have added the plots of the total computational time/agent in the scalability test section (Figure \red{xx} in the revised manuscript as also shown below). Since at each iteration, each agent only needs to update its own decision variable and some dual variables associated with the coupling constraints, we can see that the total computational time/agent is relatively low as the day-ahead problem is only solved once per day. \comment{show the new figure}}

### 2022-01-07 papers/02 journal v2/appendix.tex
g

@@

>>>>

%%%%%%%%
\algblockdefx[init]{init}{Endinit}
[1][<default value>]{\textbf{Initialization}}
[2][<default value>]{\textbf{end initialization}}

\algblockdefx[DNO]{DNO}{EndDNO}
[1][<default value>]{\textbf{DNO routine}}
[2][<default value>]{\textbf{end DNO routine}}

\algblockdefx[PRO]{PRO}{EndPRO}
[1][<default value>]{\textbf{Prosumer $i$ routine}}
[2][<default value>]{\textbf{end prosumer $i$ routine}}

\algblockdefx[Primal]{Primal}{EndPrimal}
[1][<default value>]{\textbf{primal update}}
[2][<default value>]{\textbf{end}}

\algblockdefx[Dual]{Dual}{EndDual}
[1][<default value>]{\textbf{dual update}}
[2][<default value>]{\textbf{end}}

\algblockdefx[Aux]{Aux}{EndAux}
[1][<default value>]{\textbf{auxiliary update}}
[2][<default value>]{\textbf{end}}

\algblockdefx[Comm]{Comm}{EndComm}
[1][<default value>]{\textbf{communication}}
[2][<default value>]{\textbf{end communication}}

\algblockdefx[Agg]{Agg}{EndAgg}
[1][<default value>]{\textbf{aggregation update}}
[2][<default value>]{\textbf{end}}

\algblockdefx[IUC]{IUC}{EndIUC}
[1][<default value>]{\textbf{While convergence is not achieved do:}}
[2][<default value>]{\textbf{end while}}
%%%%%%%%%%

@@

\smallskip

\begin{algorithm*}[htbp]
\caption{Semi-decentralized P2P Markets Clearing Mechanism}
\label{alg:alg1}
\begin{algorithmic}[1]
\small

\init{ }
\State
\textbf{Prosumers.} For all $i \in \mc N$: set $u_i(0) \in \mc U_i$, $\mu^{\text{tr}}_{(i,j)}(0) = \0$, $\forall j \in \mc N_i$; $\alpha_i \!<\! 
(\red{3} +N \underset{h\in \mc H}{\max}\, d_h^{\text{mg}})^{-1}$, $\beta^{\text{tr}}_{(i,j)}\! =\! \beta^{\text{tr}}_{ (j,i)} \!<\! \frac{1}{2}$, $\forall j \!\in\! \mc N_i$.
\State
\textbf{DNO.} Set $u_{N+1}(0) \!\in\! \mc U_{N+1}$, $\lambda^{\text{mg}}\!=\!\0$, $\mu^{\text{tg}} \!=\! \0$, $\mu_y^{\text{pb}}(0)\! = \!\0$, $\forall y \!\in\! \mc B$; $\alpha_{N+1} \!<\!2$, $\gamma^{\text{mg}} \!<\! \frac{1}{N}$, $\beta^{\text{tg}}\! <\! \frac{1}{|\mc N| \!+\! |\mc B|}$, $\beta_y^{\text{pb}} \!<\! \frac{1}{1\!+\!2|\mc N_y^{\mathrm{b}}|\!+\!|\mc B_y|}$,  $\forall y\!\in\! \mc B $.%

\Endinit

\smallskip
\IUC{ }
\smallskip
\ForAll{$ i \in \mc N$}
\PRO{ }
\Primal{ }
\Comment{$u_i = \{$generation, storage, main grid, trades$\}$}

\smallskip
\State 
$\psi_i(k) = 
	\col \Big(-\mu_y^{\text{pb}}(k),\edit{\mu_y^{\text{pb}}(k), -\mu_y^{\text{pb}}(k),}
	{
	%\left(
	\left[
	\begin{smallmatrix}
	I_H\\
	- I_H 
	\end{smallmatrix}
	\right] 
	%\otimes I_H
%\right)	
	}^\top \lambda^{\text{mg}}(k) + \mu^{\text{tg}}(k),
	%
	\left\{ {\mu^{\text{tr}}_{(i,j)}(k)}\right\}_{j \in \mc N_i}   \Big)$
\Comment{auxiliary vector}

\State
$u_i(k+1)   =
\left\{
\begin{array}{r l}
	\underset{\xi \in \R^{n_i}}{\argmin} & 
	\tilde J_{i} \big( \xi, \sigma^{\text{mg}}(k) \big) 
	+ {\psi_i(k)}^\top \xi + \frac{1}{2 \alpha_i}
	\left\| \xi - u_i(k) 
	\textstyle
	  \right\|^2 \\
	\text{s.t. } & \xi \in \mc U_i
\end{array} 
	\right.	$
\Comment{quadratic programming}	
\EndPrimal

\Comm{ (to DNO and trading partners)}
\State $\eta_i(k+1)= p^{\text{d}}_i-p^{\text{di}}_i(k+1)\edit{+p^{\text{ch}}_i(k+1)- p^{\text{ds}}_i(k+1)}$
\Comment{auxiliary vector: local load unbalance}
\State
$
p^{\textrm{mg}}_{i}(k+1), \eta_i(k+1)  \longrightarrow  \text{DNO,}
$
\Comment{forward to DNO}
     \ForAll{prosumer $ j \in \mc N_i$}

\State
 $p^{\text{tr}}_{(i,j)}(k+1)
	\longrightarrow \text{prosumer }j$
	\Comment{forward trade estimate to prosumer $j$}
	\EndFor
\EndComm

\Dual{ }
\Comment{reciprocity constraints}
\ForAll{$ j \in \mc N_i$}
\State
$\zeta^{\text{tr}}_{(i,j)}(k+1)  =  p^{\textrm{tr}}_{(i,j)} (k+1) + p^{\textrm{tr}}_{(j,i)} (k+1)$
\Comment{auxiliary vector}
\State
$\mu^{\text{tr}}_{(i,j)}(k+1) = \mu^{\text{tr}}_{(i,j)}(k) + \beta_{(i,j)}^{\text{tr}} \left( 
	2  \zeta^{\text{tr}}_{(i,j)}(k+1) - \zeta^{\text{tr}}_{(i,j)}(k)
	\right)$
	\Comment{reflected dual ascent}
\EndFor

\EndDual

\EndPRO

\EndFor

%%%%%%%%%%%%%%%%%%%%%%
\smallskip
%\Statex
\DNO{ }
%\State
%Iterate

\Primal{}
\Comment{angles, voltages, power on grid and buses}
\State
$\psi_{N+1}(k) = \col \left( 
	\left\{
	\0,\0,-\mu^{\text{tg}}(k) - \mu_y^{\text{pb}}(k), 
	\{ -\mu_y^{\text{pb}}(k), \0 \}_{z \in \mc B_y}
	\right\}_{y \in \mc B}
	\right)$
\Comment{auxiliary vector}

\State 	$u_{N+1}(k+1) = \proj_{\mc U_{N+1}}  \left( u_{N+1}(k) - (\alpha_{N+1})^{-1} \psi_{N+1}(k) \right)$
%\Comment{ solved via Algorithm 2 (see Appendix)}
\EndPrimal

%---------------------------Aggregation
\Agg{}
\State
$ \sigma^{\text{mg}}(k+1) = \sum_{i \in \mc N} p_i^{\text{mg}}(k+1) $
\Comment{aggregate active load, eqn. (10)}
\State
$\sigma^{\text{tg}}(k+1) = \sum_{y \in \mc B} p_y^{\text{tg}}(k+1)$
\Comment{aggregate grid-to-buses power }
\EndAgg

%---------------------------Dual Update
\Dual{}
\State
$\eta_{N+1}(k+1	) = 
	\left[
	\begin{smallmatrix}
	1\\
	- 1 
	\end{smallmatrix}
	\right] \otimes (2 \sigma^{\text{mg}}(k+1)- \sigma^{\text{mg}}(k)) 
	-
	\left[
	\begin{smallmatrix}
	\overline{p}^{\mathrm{mg}}\1_{H}-b \\
	-     \underline{p}^{\mathrm{mg}} \1_{H}+b
	\end{smallmatrix} 
	\right]  $
	\Comment{auxiliary vector}
	\State
$\lambda^{\text{mg}}(k+1) = \textstyle
	\proj_{\R^{2 H}_{\geq 0}}\left( 
	\lambda^{\text{mg}}(k) + \gamma^{\text{mg}} \eta_{N+1}(k+1)
	 \right)$
		\Comment{grid constraints}

\ForAll{buses $ y \in \mc B$}

\State
$\zeta^{\text{pb}}_y(k+1)   = \sum_{i \in \mc P_y^{\mathrm{b}}} p_i^{\mathrm{d}} + \sum_{i \in \mc N_y^{\mathrm{b}}} \eta_i(k+1)- p^{\text{tg}}_y(k+1) - \sum_{z \in \mc B_y} p^\ell_{(y,z)} (k+1)$
\Comment{auxiliary vector}

\State
$\mu_y^{\text{pb}}(k+1) = \mu_y^{\text{pb}}(k) + \beta^{\text{pb}}_y (2 \zeta^{\text{pb}}_y(k+1)- \zeta^{\text{pb}}_y(k))$
\Comment{local power balance of bus $y$}
\EndFor

\State
$\zeta^{\text{tg}}(k+1) = \sigma^{\text{mg}}
	(k+1)+b- \sigma^{\text{tg}}(k+1)$
\Comment{auxiliary vector}

\State
$\mu^{\text{tg}}(k+1) = \mu^{\text{tg}}(k) + \beta^{\text{tg}} (2\zeta^{\text{tg}}(k+1)-\zeta^{\text{tg}}(k))$
\Comment{grid-to-buses constraints}
\EndDual

\Comm{ (broadcast to all prosumers)}
\State
$ \{ \sigma^{\mathrm{mg}}(k+1)+b, \, \lambda^{\text{mg}}(k+1), \mu^{\text{tg}}(k+1) \} 
	\longrightarrow  \mc N$
\ForAll{buses $ y \in \mc B$}
\State
$\mu^{\text{pb}}_y(k+1)\longrightarrow \mc N_y^{\mathrm{b}}$
\Comment{only to prosumers on bus $y$}
\EndFor

\EndComm

\EndDNO

\EndIUC

\end{algorithmic}
\end{algorithm*}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
